Supplemental Materials for: Meta-analytic approaches and new effect sizes to account for heterogeneous effects in comparative physiology

### 2021-07-15 MS/supp.Rmd
Fixing Patrice's code a bit, and code chunks. Just to get it working. Problems with VCV matrix (might even be too complex)

```{r loadpackages, echo = TRUE, results = "hide", messages = FALSE, class.source='klippy'}
#install.packages("pacman")
#devtools::install_github("itchyshin/orchard_plot", subdir = "orchaRd", force = TRUE)
pacman::p_load(devtools, png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd, here, osfr, magrittr)
```

@@

```{r class.source='klippy'}

@@

# Load the data file
data_CS1a <- read.csv(here::here("ms", "CTmax_ARR.csv"))
```

@@

```{r, class.source='klippy', results = 'hide'}
# Variance covariance matrix to account for non-independence of measurements performed on the same cohorts of animals
VCV_ARR<- metaAidR::make_VCV_matrix(data_CS1a, V = "Var_ARR", cluster = "shared_measurement_ID", obs = "es_ID")
```

@@

```{r, class.source='klippy', results = 'hide'}
# Multi-level meta-analytic model
Model_CS1a_MLMA<-metafor::rma.mv(yi=ARR~-1, V=VCV_ARR, 
                   method="REML",
                   random=list(~1|species_ID,
                               ~1|es_ID), 
                   test="t",
                   dfs = "contain",
                   data=data_CS1a)
summary(Model_CS1a_MLMA)

# Calculate Prediction Intervals
PIs_CS1a_MLMA <- predict(model_CS1a_MLMA)
print(PIs_CS1a_MLMA)

@@

## Multi-level Meta-analysis of slope differences between two groups

@@

```{r class.source='klippy'}
# Download the data file from OSF
osfr::osf_retrieve_file("https://osf.io/zubky/") %>% osfr::osf_download(conflicts = "overwrite")

# Load the data file
data_CS1b <- read.csv(here::here("ms", "CTmax_ARR_sex.csv"))
```

### Calculate effect size

@@

Again, we first started by accounting for the non-independence of CTmax estimates measured on the same cohorts using a variance-covariance matrix termed as `VCV_ARRD`. 
We then fit a multi-level meta-analytic model using a similar structure as demonstrated before. 
Note that this model can be extended to meta-regressions by fitting moderator variables. 
```{r, class.source='klippy', results = 'hide'}

# Variance covariance matrix to account for non-independence of measurements performed on the same cohorts of animals
VCV_ARRD<- metaAidR::make_VCV_matrix(data_CS1b, V = "Var_ARR", cluster = "shared_measurement_ID", obs = "es_ID")

# Multi-level meta-analytic model
model_CS1b_MLMA<-metafor::rma.mv(yi=ARRD~-1, V=VCV_ARRD, 
                   method="REML",
                   random=list(~1|species_ID,
                               ~1|es_ID), 
                   test="t",
                   dfs = "contain",
                   data=data_CS1b)
print(model_CS1b_MLMA)

@@

```{r}
pander(sessionInfo(), locale = FALSE)
```

>>>>

```{r loadpackages, echo = TRUE, results = "hide", messages = FALSE, class.source='klippy'}
#install.packages("pacman")
#devtools::install_github("itchyshin/orchard_plot", subdir = "orchaRd", force = TRUE)
#devtools::install_github("daniel1noble/metaAidR")
pacman::p_load(devtools, png, jpeg, pander, cowplot, flextable, tidyverse, metafor, orchaRd, here, osfr, magrittr, metaAidR)
```

@@

```{r class.source='klippy', results = 'hide'}

@@

# Load the data file
data_CS1a <- read.csv(here::here("CTmax_ARR.csv"))
```

@@

```{r, class.source='klippy', results = 'hide', message=FALSE}
# Variance covariance matrix to account for non-independence of measurements performed on the same cohorts of animals
VCV_ARR<- metaAidR::make_VCV_matrix(data_CS1a, V = "Var_ARR", cluster = "shared_measurement_ID", obs = "es_ID")

# This method should be similar from clubSandwich
VCV_ARR2 <- clubSandwich::impute_covariance_matrix(data_CS1a$Var_ARR, cluster = "shared_measurement_ID", r =0.5)
```

@@

```{r, class.source='klippy'}
# Multi-level meta-analytic model
Model_CS1a_MLMA <- metafor::rma.mv(ARR ~ 1, V = VCV_ARR2, 
                   method="REML",
                   random=list(~1|species_ID,
                               ~1|es_ID), 
                   test="t",
                   dfs = "contain",
                   data=data_CS1a)
summary(Model_CS1a_MLMA)

# Calculate Prediction Intervals
PIs_CS1a_MLMA <- predict(Model_CS1a_MLMA)
print(PIs_CS1a_MLMA)

@@

## Multi-level Meta-analysis of Slope Differences between Two Groups

@@

```{r class.source='klippy', results = 'hide'}
# Download the data file from OSF
osfr::osf_retrieve_file("https://osf.io/zubky/") %>% osfr::osf_download(conflicts = "overwrite")

# Load the data file
data_CS1b <- read.csv(here::here("CTmax_ARR_sex.csv"))
```

@@

Again, we first started by accounting for the non-independence of CTmax estimates measured on the same cohorts using a variance-covariance matrix termed as `VCV_ARRD`.

```{r, class.source='klippy',  results = 'hide', message=FALSE}
# Variance covariance matrix to account for non-independence of measurements performed on the same cohorts of animals
#VCV_ARRD<- metaAidR::make_VCV_matrix(data_CS1b, V = "Var_ARR", cluster = "shared_measurement_ID", obs = "es_ID")
VCV_ARRD <- clubSandwich::impute_covariance_matrix(data_CS1b$Var_ARRD, cluster = "shared_measurement_ID", r =0.5)
```

We then fit a multi-level meta-analytic model using a similar structure as demonstrated before. 
Note that this model can be extended to meta-regressions by fitting moderator variables.

```{r, class.source='klippy'}
# Multi-level meta-analytic model
model_CS1b_MLMA<-metafor::rma.mv(yi= ARRD~ 1, V = VCV_ARRD, 
                   method="REML",
                   random=list(~1|species_ID,
                               ~1|es_ID), 
                   test="t",
                   dfs = "contain",
                   data=data_CS1b)
print(model_CS1b_MLMA)

@@

```{r, echo = FALSE}
pander(sessionInfo(), locale = FALSE)
```
